Polytope notes

### 2019-11-30 notes/bo-separated.tex
started proof...
working on separated link improved proof

(Bo, 2019-11-13)

\begin{theorem}
  Let $L(\cdot;p)$ be a polyhedral function with $U^* := \arg\min_{u} L(u;p)$.
  Then there exists $c > 0$ such that $L(u;p) \geq c \cdot \|U^* - u\|_2$ for all $u$.
\end{theorem}
\begin{proof}
  Consider the epigraph of $L(\cdot;p)$, a polyhedral set (intersection of finitely many halfspaces).
  Recall that each face of the epigraph is uniquely identified by a subset of constraints which are tight for exactly that face.
  In particular, $U^*$ is a face (as it is the set of points exposed by the ``downward'' direction), identified by some subset $S$.

  Now consider all faces that are proper subsets of $U^*$; they are identified by all supersets $S' \supsetneq S$ of constraints.
  We claim $U^*$ is the union of the relative interiors of these faces.

  [To be continued...]
\end{proof}

>>>>

(Bo, 2019-11-13 and continuing)

\begin{theorem}
  Let $L(\cdot;p)$ be a polyhedral function with $U^* := \arg\min_{u} L(u;p)$.
  Then there exists $c > 0$ such that $L(u;p) \geq c \cdot \|U^* - u\|_2$ for all $u$.
\end{theorem}
\begin{proof}
  Consider the epigraph of $L(\cdot;p)$, a polyhedral set (intersection of finitely many halfspaces).
  Recall that each face $F_S$ of the epigraph is uniquely identified by a subset of constraints $S$ which are tight for exactly that face.
  In particular, $U^*$ is a face (as it is the set of points exposed by the ``downward'' direction), identified by some subset $S^*$.

  Now consider all faces that are proper subsets of $U^*$; they are identified by all supersets $S \supsetneq S^*$ of constraints.

  Claim: the relative boundary of $U^*$ is the disjoint union of the relative interiors of these faces $U_S : S \supsetneq S^*$.
  (This follows because $U^*$ is the disjoint union of relative interiors of faces $U_S: S \supseteq S^*$.)

  Now, let $U_S' = \text{relint}~U_S$.

  Claim: the set of normals and tangent supporting hyperplanes at $u$ is constant for all $u \in U_S'$, for each $U_S'$.
  Furthermore, each is a closed, convex, bounded (?) set.

  For each $u \not\in U^*$, write $u^*(u)$ for the projection of $u$ onto $U^*$ and write $S(u)$ for the $S$ such that $u \in U_S'$.
  Write $u = u^*(u) + \alpha(u) v(u)$ where $v$ is a unit vector.

  Then $L(u;p) - L^* \geq \max_d \alpha(u) d \cdot v(u)$ where $d$ ranges over all subgradients of $L^*$ at $u^*(u)$.
  For each face indexed by $S$ and each normal $v$, we have $\max_d d \cdot v > 0$. (Otherwise, contradiction.)
  Note the function $v \mapsto \max_d d \cdot v$ is continuous because $d$ is a compact set (?).
  Because the set of normals $v$ is compact, $\inf_v \max_d d \cdot v = \min_v \max_d d \cdot v > 0$.

  [To be improved...]
\end{proof}
